Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-17 analysis/paper/shceof.Rmd
Agrega unas palabras sobre primavera

<!-- cambiarn nomenclatura. Imaginario / real -> pasarlo a nombrar la fase -->

<!-- Chequear con ncep -->

<!-- The following code chunk defines some general settings how code chunks should behave. -->

@@

One of the main features of the zonally asymmetric circulation are the Pacific--South American Patterns [@mo2001], which are associated with precipitation anomalies in South America.
Besides, @raphael2007 suggests that variability in the planetary wave 3 projected onto its climatological location is associated with Antarctic sea ice concentration anomalies.
@irving2015 showed that planetary wave amplitude in general is associated sea ice concentration, as well as temperature and precipitation anomalies.

>>>>

@@

One of the main features of the zonally asymmetric circulation are the Pacific--South American Patterns [@mo2001], which are associated with precipitation anomalies in South America, particularly in the September-October-November trimester (cita).
Besides, @raphael2007 suggests that variability in the planetary wave 3 projected onto its climatological location is associated with Antarctic sea ice concentration anomalies.
@irving2015 showed that planetary wave amplitude in general is associated sea ice concentration, as well as temperature and precipitation anomalies.
